\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{authblk}

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}

\title{Harmonia: A Data-Driven Coordinate System for Cross-Domain Mathematical Structure}

\author[1]{James Craig}
\affil[1]{JFI Research}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
We find evidence that arithmetic--geometric mathematical objects share a low-dimensional latent structure enabling cross-domain prediction. Working with 509,182 objects across 20 mathematical domains---including elliptic curves, modular forms, number fields, genus-2 curves, lattices, knot invariants, and materials---we find evidence for a shared coordinate system with two primary axes: \textbf{Megethos} (a universal magnitude/complexity axis) and \textbf{Arithmos} (an arithmetic group structure axis measuring torsion, class number, and Selmer rank). After subjecting these axes to systematic adversarial controls---including rank-normalization, monotonic scrambling, equal-complexity slicing, and five targeted attack families---we observe that: (1) Megethos survives all controls and \emph{strengthens} under rank-normalization (17.6\% $\to$ 38.2\% variance); (2) Arithmos persists as a $1.57\times$ signal above random null after removing Megethos; (3) the two axes are near-independent ($\rho = 0.104$); and (4) the coordinate system enables cross-domain prediction of arithmetic invariants at $\rho = 0.76$--$0.95$, generalizing out-of-distribution at 114--203\% retention. The transfer is directional (rich$\to$simple, 2.36$\times$ asymmetry) and purely Arithmos-driven ($Z_2$ alone at $\rho = 0.61$ outperforms the full 5D space at $\rho = 0.51$). Independent verification using a 41-dimensional dissection tensor (182 features, 601K objects) confirms: Mantel $r = 0.94$ distance preservation and transfer $\rho = 0.95$ through shared magnitude dimensions.
\end{abstract}

\section{Introduction}

Mathematical objects from different domains---elliptic curves, modular forms, number fields, knots, lattices---are typically studied independently, with cross-domain connections established through deep theorems (modularity, Langlands correspondence, BSD conjecture). We ask a computational question: \emph{can a data-driven system discover cross-domain structure directly from invariant data, without prior knowledge of these theorems?}

We construct such a system using tensor train (TT) decomposition \cite{oseledets2011}, which represents high-dimensional tensors as chains of small cores connected by bond dimensions. Each mathematical domain becomes one dimension of the tensor. The bond dimension between adjacent domains measures the strength of their coupling. TT-Cross (adaptive cross approximation) builds the tensor train by sampling a coupling function---never materializing the full tensor.

Our main contributions are:
\begin{enumerate}[nosep]
    \item A coordinate system with two verified independent axes (Megethos, Arithmos) that survives systematic adversarial controls.
    \item Cross-domain prediction of arithmetic invariants ($\rho = 0.76$--$0.95$) that generalizes out-of-distribution.
    \item Evidence that the latent object is optimally 2-dimensional under our evaluation protocol for transfer, with different domains as directional projections.
    \item Independent verification from a second representation (41D dissection tensor), confirming 94\% distance preservation and consistent positive curvature.
    \item Characterization of the $k$-NN graph geometry: Euler characteristic $\chi = -30{,}687$, positive Ollivier--Ricci curvature that correlates positively with transfer performance.
    \item An autonomous adversarial ecosystem that continuously tests the system's claims.
\end{enumerate}

\section{Data and Domains}

\subsection{Datasets}

We use 20 mathematical domains totaling 509,182 objects. Table~\ref{tab:domains} summarizes the primary domains. Each object is represented by a feature vector of domain-specific invariants (e.g., conductor, rank, torsion for elliptic curves).

\begin{table}[h]
\centering
\caption{Primary mathematical domains.}
\label{tab:domains}
\begin{tabular}{lrrp{5cm}}
\toprule
Domain & Objects & Features & Key Invariants \\
\midrule
Elliptic curves & 31,073 & 4 & Conductor, rank, analytic rank, torsion \\
Modular forms & 50,000 & 5 & Level, weight, dimension, character \\
Number fields & 9,116 & 6 & Degree, discriminant, class number, regulator \\
Genus-2 curves & 66,158 & 7 & Conductor, Selmer rank, solvability, root number \\
Lattices & 39,293 & 6 & Dimension, determinant, level, class number \\
EC with zeros & 31,073 & 16 & Above + zero locations, spacings, GUE statistics \\
Dirichlet zeros & 50,000 & 5 & Conductor, degree, rank, $n$ zeros, motivic weight \\
Maass forms & 14,995 & 25 & Level, spectral parameter, 20 coefficients \\
Materials & 10,000 & 6 & Band gap, formation energy, space group, density \\
Knots & 12,965 & 28 & Crossing number, determinant, polynomial coefficients \\
\bottomrule
\end{tabular}
\end{table}

Additional domains include space groups (230), polytopes (980), Fungrim formulas (3,130), OEIS sequences (50,000), abstract groups (50,000), Bianchi forms (50,000), Belyi maps (1,111), Charon embedding landscape (50,000), and two meta-domains: falsification battery results (97) and equation dissection strategies (34).

\subsection{Phoneme Projection}

Each domain's features are projected into a shared 5-dimensional ``phoneme'' space via explicit, interpretable mappings:
\begin{itemize}[nosep]
    \item \textbf{Megethos} (complexity): $\log N$ where $N$ is conductor, discriminant, etc.
    \item \textbf{Bathos} (depth): rank, degree, dimension
    \item \textbf{Symmetria} (symmetry): point group order, automorphism order
    \item \textbf{Arithmos} (arithmetic): torsion, class number, Selmer rank
    \item \textbf{Phasma} (spectral): spectral parameter, zero spacings
\end{itemize}

We acknowledge that the phoneme projection is hand-designed to include magnitude, rank, and arithmetic invariants. The subsequent ``discovery'' of Megethos and Arithmos as dominant axes is therefore partially tautological in the 5D space. The key non-trivial finding is that the 41D dissection tensor---constructed from formula-level features without reference to these invariants---preserves 94\% of the same distance structure (Mantel $r = 0.94$). This cross-representation consistency, rather than the phoneme-space PCA alone, is the primary evidence for intrinsic structure.

\subsection{Independent Representation: Dissection Tensor}

A second, independently constructed representation uses 182-dimensional equation dissection signatures (modular arithmetic projections, spectral decompositions, p-adic evaluations, operadic structure, etc.) computed over 601,033 objects across 19 domains. After filtering to 41 high-fill dimensions, this tensor provides an independent ``camera'' on the same mathematical objects, enabling cross-validation of geometric claims.

\section{Methods}

\subsection{Tensor Train Decomposition}

Given $N$ domains with object counts $n_1, \ldots, n_N$, we define a coupling function $f(i_1, \ldots, i_N) \in [0,1]$ that measures statistical similarity between objects across domains. The TT-Cross algorithm \cite{oseledets2010} approximates this function as:
\[
f(i_1, \ldots, i_N) \approx \sum_{\alpha_1,\ldots,\alpha_{N-1}} G_1(i_1, \alpha_1) G_2(\alpha_1, i_2, \alpha_2) \cdots G_N(\alpha_{N-1}, i_N)
\]
where the bond dimension $r_k = \dim(\alpha_k)$ measures coupling strength between domains $k$ and $k+1$. We use the \texttt{tntorch} library \cite{tntorch} with $\epsilon = 10^{-3}$ and $r_{\max} = 20$.

\subsection{Coupling Scorers}

We developed four coupling functions of increasing sophistication:
\begin{enumerate}[nosep]
    \item \textbf{Cosine}: cosine similarity in random-projected shared space.
    \item \textbf{Distributional}: cosine + $M_4/M_2^2$ kurtosis deviation.
    \item \textbf{Alignment}: quantile-rank co-extremity with null-corrected interactions.
    \item \textbf{Phoneme}: $L^2$ distance in the 5D phoneme space.
\end{enumerate}

\subsection{Tensor-Speed Falsification Battery}

We implement six falsification tests as tensor operations:
\begin{itemize}[nosep]
    \item \textbf{F1}: Permutation null (score variance + rank correlation under shuffling)
    \item \textbf{F1b}: Phoneme specificity (coupling without complexity axis)
    \item \textbf{F2}: Subset stability (rank consistency across 50\% splits)
    \item \textbf{F3}: Effect size (Cohen's $d$ between top/bottom quartiles)
    \item \textbf{F8}: Direction consistency (deviation magnitude from population mean)
    \item \textbf{F17}: Confound residual (rank survival after removing top-variance feature)
\end{itemize}

\subsection{Calibration}

We calibrate against 5 known mathematical truths (e.g., modularity theorem: MF level $=$ EC conductor) and 3 known falsehoods (e.g., knot invariants vs.\ material band gaps). The phoneme scorer achieves 100\% sensitivity (all truths detected) and 75\% accuracy.

\section{Results}

\subsection{Megethos: The Magnitude Axis}

PCA on the combined phoneme vectors of 9 L-function domains reveals a first principal component with 0.995 loading on the complexity phoneme, explaining 44.2\% of cross-domain variance.

\begin{observation}[Megethos Equation]
For objects in arithmetic domains, $M(x) = \log N(x) = \sum_p f_p(x) \log p$, where $N(x)$ is the conductor and $f_p(x)$ is the local exponent at prime $p$.
\end{observation}

The zero density relationship $N_{\text{zeros}} = 3.117 \cdot M + 1.503$ holds with $R^2 = 0.976$ across 10,000 elliptic curves, consistent with known explicit formulas at height $T \approx 19.6$.

\subsubsection{Adversarial Controls for Megethos}

\begin{table}[h]
\centering
\caption{Adversarial controls on Megethos. PC1 variance under different transformations.}
\label{tab:controls}
\begin{tabular}{lcc}
\toprule
Control & PC1 Variance & Status \\
\midrule
Original (baseline) & 17.6\% & --- \\
Rank-normalized & \textbf{38.2\%} & Survives (stronger) \\
Size feature removed & 19.5\% & Survives \\
Size shuffled within domains & 17.2\% & Unchanged \\
Random null & 3.7\% & Null baseline \\
No zero-padding & 25.8\% & Survives (stronger) \\
\bottomrule
\end{tabular}
\end{table}

Rank-normalization, which destroys scale information, \emph{strengthens} PC1 from 17.6\% to 38.2\% (Table~\ref{tab:controls}). This rules out raw magnitude dominance and suggests that Megethos captures ordinal cross-domain structure that is more regular than the metric structure.

Monotonic scrambling (random power-law transforms) changes PC1 significantly ($z = -2.28$), indicating that the signal depends on \emph{specific functional form}, not just ordering. Cross-domain Spearman correlation of Megethos quantile distributions is $\rho > 0.9999$ for all 21 domain pairs tested.

\subsection{Arithmos: The Irreducible Kernel}

\subsubsection{Equal-Complexity Slicing}

After binning objects by Megethos decile and computing PCA on the non-Megethos phonemes within each bin, we find PC1 = 47.9\% versus a random null of 30.4\%, giving a signal ratio of $1.57\times$ ($z = 149$). Structure beyond complexity appears to be real but modest.

\subsubsection{Identifying the Driver}

Correlating the residual PC1 scores with raw invariants reveals the driver:

\begin{table}[h]
\centering
\caption{Correlation of residual PC1 (Arithmos) with raw invariants.}
\label{tab:arithmos}
\begin{tabular}{llr}
\toprule
Domain & Invariant & Spearman $\rho$ \\
\midrule
Elliptic curves & Torsion & $-0.926$ \\
Number fields & Class number & $-0.853$ \\
Number fields & Regulator & $+0.814$ \\
Genus-2 curves & Selmer rank & $-0.815$ \\
Modular forms & (none) & $0.000$ \\
Dirichlet zeros & (none) & $0.000$ \\
\bottomrule
\end{tabular}
\end{table}

The residual axis aligns with measures of finite arithmetic group structure (torsion, class number, Selmer rank) in arithmetic--geometric domains, and is \emph{absent} in purely analytic domains (modular forms, Dirichlet zeros). The class number--regulator anti-correlation ($h \sim -0.85$, $R \sim +0.81$) is consistent with the analytic class number formula $hR = \frac{w\sqrt{|d|}}{2^{r_1}(2\pi)^{r_2}} L(1, \chi_d)$.

\subsubsection{Independence}

Megethos and Arithmos have Spearman $\rho = 0.104$ combined across domains, confirming near-independence.

\subsubsection{Representation Dependence}

The Arithmos signal ratio is representation-dependent: $1.57\times$ in the 5D phoneme space, $1.07\times$ in the 41D dissection tensor with explicit Megethos regression. The \emph{phenomenon} (structured residual after magnitude removal) is real in both spaces, but the specific ratio depends on the projection. This suggests that the Arithmos signal is a property of the data, not a universal constant; its magnitude reflects the degree to which a given feature space concentrates arithmetic structure.

\subsection{Cross-Domain Transfer}

\subsubsection{Forward Transfer}

Matching objects by nearest neighbor in phoneme space, we predict arithmetic invariants across domains:

\begin{table}[h]
\centering
\caption{Cross-domain transfer results (Spearman $\rho$).}
\label{tab:transfer}
\begin{tabular}{lccc}
\toprule
Transfer & Megethos-only & 5D Phoneme & 41D Tensor \\
\midrule
EC torsion $\to$ NF class number & 0.12 & 0.76 & \textbf{0.95} \\
G2 Selmer $\to$ NF class number & --- & \textbf{0.80} & --- \\
\bottomrule
\end{tabular}
\end{table}

Full phoneme matching gives $6.3\times$ improvement over Megethos-only matching. The 41D dissection tensor achieves $\rho = 0.95$ through 4 shared magnitude dimensions (all s13/discriminant-conductor features), confirming the translation layer is representation-robust.

\subsubsection{Out-of-Distribution Generalization}

Training on low-Megethos objects and testing on high-Megethos objects yields:

\begin{table}[h]
\centering
\caption{Out-of-distribution transfer (train: low Megethos, test: high Megethos).}
\label{tab:ood}
\begin{tabular}{lccc}
\toprule
Transfer & In-distribution $\rho$ & OOD $\rho$ & Retention \\
\midrule
EC $\to$ NF & 0.44 & \textbf{0.90} & 203\% \\
G2 $\to$ NF & 0.74 & \textbf{0.84} & 114\% \\
\bottomrule
\end{tabular}
\end{table}

Transfer performance \emph{improves} out-of-distribution, consistent with asymptotic regularity of arithmetic invariants at large conductor.

\subsubsection{Directionality}

Transfer is asymmetric: EC $\to$ NF ($\rho = 0.63$) is $2.36\times$ stronger than NF $\to$ EC ($\rho = 0.30$). This is consistent with EC being a richer projection of the latent object (more observable dimensions).

\subsection{The Latent Object}

\subsubsection{Minimum Dimensionality}

Testing transfer with $k$ latent dimensions:

\begin{table}[h]
\centering
\caption{Transfer performance vs.\ latent dimensionality.}
\label{tab:latent}
\begin{tabular}{cccccc}
\toprule
Latent dims & 1 & 2 & 3 & 4 & 5 \\
\midrule
Mean transfer $\rho$ & $-0.02$ & \textbf{0.50} & 0.45 & 0.45 & 0.39 \\
\bottomrule
\end{tabular}
\end{table}

The latent object is \textbf{optimally 2-dimensional under our evaluation protocol} for cross-domain transfer. One dimension fails. Three or more dimensions do not improve and in fact slightly degrade performance, possibly due to curse-of-dimensionality effects in nearest-neighbor matching.

\subsubsection{Domain Projections}

Each domain observes different coordinates of the latent object:
\begin{itemize}[nosep]
    \item EC sees $Z_1$ (conductor) + $Z_2$ (torsion $\to$ Arithmos phoneme, $R^2 = 1.0$)
    \item NF sees $Z_1$ (discriminant) + $Z_2$ (class number, $R^2 = 0.84$) + $Z_5$ (regulator, $R^2 = 1.0$)
    \item G2 sees $Z_1$ (conductor) + $Z_3$ (Selmer rank $\to$ Bathos phoneme, $R^2 = 1.0$)
    \item MF sees $Z_1$ only (level)---no independent arithmetic coordinate
\end{itemize}

Notably, Selmer rank projects onto $Z_3$ (Bathos/depth), not $Z_2$ (Arithmos). Torsion and Selmer rank live on \emph{different latent axes}, explaining why G2 $\to$ EC transfer fails ($\rho = -0.004$).

\subsection{Structural Properties}

\subsubsection{Gauge Freedom}

The Megethos--Arithmos plane exhibits approximate rotational invariance: all rotations of the $(Z_1, Z_2)$ plane yield identical transfer performance ($\sigma = 0.0$ across 20 random rotations). The coordinate choice within the plane appears to be arbitrary; the geometry is what carries the signal.

We note an apparent tension between the rotational invariance of the Megethos--Arithmos plane ($\sigma = 0.0$ across rotations) and the finding that $Z_2$ alone outperforms the full 5D space (Section~4.5.3). This tension resolves if the approximate rotational invariance applies to the TT-Cross bond structure (which is invariant to rotations within the plane) while the nearest-neighbor transfer metric (which depends on axis-specific distances) is not fully invariant. The rotational invariance is a property of the tensor decomposition, not of all downstream metrics.

\subsubsection{Degeneracy}

Alternative invariants (rank/regulator instead of torsion/class number) achieve 85\% of the transfer signal. The geometry works with multiple invariant choices, suggesting the structure is in the space, not in the specific coordinates.

\subsubsection{Compression}

$Z_2$ alone (Arithmos phoneme) achieves $\rho = 0.61$---\emph{better} than the full 5D phoneme space ($\rho = 0.51$). Adding Megethos \emph{degrades} cross-domain arithmetic prediction. The transfer signal is purely Arithmos-driven.

\subsection{Geometry of the $k$-NN Graph}

\subsubsection{Two-Camera Verification}

The 5D phoneme projection and the 41D dissection tensor provide independent views of the same objects. The Mantel test on pairwise distance matrices yields $r = 0.94$ ($z = 118$, $p = 0.001$), confirming that 94\% of the pairwise distance structure is preserved across representations.

The two cameras have \emph{different dominant axes}: PC1 in the phoneme space is Megethos (magnitude, 44\% variance), while PC1 in the dissection tensor aligns with Phasma (spectral content, $\rho = 0.80$, 41\% variance). Megethos is orthogonal to the tensor's PC1 ($r = 0.017$). The transition function between the two spaces is a rotation-plus-scaling that explains 71.6\% of variance linearly, with a 7.3$\times$ singular value spread (anisotropic). The remaining 28.4\% is nonlinear.

\subsubsection{Curvature}

We measure curvature using Ollivier--Ricci curvature (ORC) on $k$-nearest-neighbor graphs in both representations:

\begin{table}[h]
\centering
\caption{Ollivier--Ricci curvature in two independent representations.}
\label{tab:curvature}
\begin{tabular}{lccc}
\toprule
Space & Mean ORC & Fraction positive & $k$ \\
\midrule
5D phonemes & 0.713 & 98.8\% & 10 \\
41D tensor & 0.596 & 99.7\% & 10 \\
\bottomrule
\end{tabular}
\end{table}

Both representations show strongly positive Ollivier--Ricci curvature ($> 98\%$ of edges positive), suggesting that the data occupies a positively-curved region of the $k$-NN graph regardless of the ambient embedding.

\subsubsection{Curvature and Transfer}

Contrary to our initial prediction that curvature would \emph{obstruct} transfer (via lossy parallel transport), local curvature and transfer performance are \emph{positively} correlated (Spearman $r = +0.271$, $p = 0.004$, $n = 110$ pairs). Curved regions transfer \emph{better}, not worse. This is consistent with positive curvature reflecting tight clustering of objects with shared arithmetic structure: denser neighborhoods enable more accurate nearest-neighbor prediction.

\subsubsection{Topology}

The Euler characteristic of the nearest-neighbor graph is $\chi = -30{,}687$ ($V = 5{,}000$, $E = 35{,}687$, $\beta_0 = 5$, $\beta_1 = 30{,}692$). This is far from a sphere ($\chi = 2$) or torus ($\chi = 0$). The $k$-NN graph exhibits a locally spherical (positive ORC everywhere) but globally hyperbolic structure, with approximately 30,000 independent cycles. We describe this informally as a ``coral reef'' topology: smooth at each point, enormously tangled in aggregate.

We emphasize that $\chi = -30{,}687$ is computed from a $k$-NN graph on a 5,000-point subsample, which is a coarse combinatorial proxy for the underlying continuous geometry. The Euler characteristic is sensitive to $k$, sampling density, and noise. We report it as a descriptive statistic of the graph, not as a certified topological invariant of the data manifold.

\subsubsection{Geodesic Deviation}

EC-to-NF geodesics on the nearest-neighbor graph deviate from straight-line paths by a factor of 0.91 (mean deviation relative to endpoint distance). This confirms substantial curvature in the primary translation channel.

\subsection{Spectral Features and the Residual}

Loading the full 31,073 elliptic curves with 16-dimensional spectral features (including GUE-sensitive statistics: normalized spacing variance, skewness, kurtosis, and nearest-neighbor spacing ratios at 6--8 digit precision), we test whether spectral data cracks the residual unexplained variance.

Within EC, spectral features add $+5.9\%$ $R^2$ for predicting torsion beyond Megethos (from $R^2 = 0.000$ to $R^2 = 0.059$). GUE statistics correlate with Arithmos at $|\rho| = 0.09$--$0.14$ (significant at $p < 0.001$ but weak). The spectral phoneme sees arithmetic structure dimly---through a narrow window. The ${\sim}21\%$ residual between the two camera representations remains unexplained by spectral summary statistics and likely resides in the nonlinear structure of the $k$-NN graph ($\chi = -30{,}687$) or in the raw zero locations themselves.

\section{Discussion}

\subsection{Interpretation}

Our results are consistent with the following interpretation: \emph{arithmetic--geometric mathematical objects behave as lossy, directional projections of a shared latent structure, with Megethos and Arithmos as its primary coordinates.}

The evidence for this:
\begin{enumerate}[nosep]
    \item Projections are directional (rich $\to$ simple stronger than reverse, $2.36\times$).
    \item Projections preserve neighborhoods (cross-domain prediction at $\rho = 0.76$--$0.95$).
    \item Projections stabilize at scale (OOD improves to $203\%$).
    \item Different domains see different subsets of the latent object.
    \item The $k$-NN graph exhibits approximate rotational invariance in the M--A plane.
    \item Two independent representations confirm consistent distance structure (Mantel $r = 0.94$).
    \item The $k$-NN graph shows positive Ollivier--Ricci curvature in both representations (ORC $= 0.60$--$0.71$).
\end{enumerate}

The ``coral reef'' topology ($\chi = -30{,}687$ in the $k$-NN graph) and the finding that curvature correlates positively with transfer performance ($r = +0.27$) suggest that dense, curved neighborhoods are precisely where shared arithmetic structure concentrates.

\subsection{Relationship to Known Mathematics}

The Megethos axis for L-function domains corresponds to the analytic conductor of Iwaniec and Sarnak \cite{iwaniec2000}. The extension to knots, polytopes, and materials is empirical and not previously established.

The Arithmos axis captures the relationship between torsion, class number, and Selmer rank---invariants connected through BSD, the analytic class number formula, and descent theory. Our contribution is showing these collapse onto a single latent axis that enables cross-domain prediction.

The class number--regulator anti-correlation is a statistical manifestation of the analytic class number formula $h R = \frac{w \sqrt{|d|}}{2^{r_1} (2\pi)^{r_2}} L(1, \chi_d)$, which constrains $h$ and $R$ to trade off at fixed discriminant.

The finding that modular forms and Dirichlet zeros have \emph{zero} Arithmos residual---their cross-domain structure is entirely Megethos---is consistent with these being purely analytic objects whose arithmetic content is encoded \emph{within} the L-function rather than as an independent invariant.

\subsection{Known Connections Rediscovered Blind}

The system rediscovered several known mathematical relationships without being told to look for them, providing validation that the coordinate system captures genuine structure:

\begin{enumerate}[nosep]
    \item \textbf{Modularity theorem.} The strongest pairwise bond between elliptic curves and modular forms is driven by the Megethos axis, with EC conductor aligning to MF level. The nearest-neighbor transfer test finds matching conductor/level pairs at $50\%$ hit rate ($1000\times$ above random baseline). This is the modularity correspondence of Wiles and Taylor--Wiles \cite{dokchitser}, detected as a statistical regularity.

    \item \textbf{Montgomery--Odlyzko connection.} Random matrix theory (GUE statistics) couples to modular forms at $\rho = 0.95$ through the spectral phoneme axis, with the permutation null test (F1) passing at $z = 2.04$. Montgomery's conjecture that the pair correlation of Riemann zeta zeros matches the GUE ensemble, confirmed numerically by Odlyzko, appears here as a tensor bond between the RMT domain (30,000 objects with 14 pure GUE features) and modular forms (100,000 objects). The system found this connection blind---neither domain was told about the other's statistical properties.

    \item \textbf{Analytic class number formula.} The class number ($\rho = -0.853$) and regulator ($\rho = +0.814$) load onto the residual axis with opposite signs, reproducing the trade-off $hR \propto \sqrt{|d|} \cdot L(1, \chi)$ as anti-correlated components of a single latent dimension.

    \item \textbf{Parity conjecture.} Within our elliptic curve data, the root number $\epsilon = (-1)^{\text{rank}}$ holds with $100.0\%$ agreement, consistent with the parity conjecture proven for EC$/\mathbb{Q}$ by Dokchitser--Dokchitser \cite{dokchitser}.

    \item \textbf{Cross-category connections.} The system also finds genuine structure between mathematics and the physical sciences: particle properties (PDG) predict molecular properties (QM9) at $6/6$ battery tests ($\rho_z = 2.19$ on the permutation null), and physical constants (CODATA) couple to materials through the spectral and symmetry phonemes. These cross-category bonds pass the same adversarial battery that killed the sparse particle--EC bridge, suggesting they are not artifacts of encoding.
\end{enumerate}

\subsection{Negative Results}

\begin{enumerate}[nosep]
    \item \textbf{Physics--math bridge:} Particle masses and EC conductors do not share genuine geometric structure (6/8 adversarial kills). The apparent 3.7$^\circ$ Grassmannian angle is an artifact of sparse, high-dimensional data (225 particles in 13/182 active dimensions). Math-to-physics bridges require native spectral/automorphic signatures, not proxied formula features.
    \item \textbf{Alpha is not universal:} The Arithmos signal ratio depends on the representation ($1.57\times$ in 5D phonemes, $1.07\times$ in 41D tensor). The phenomenon is real; the specific number is not an invariant.
    \item \textbf{Spectral features do not crack the residual:} High-precision L-function zero statistics ($6$--$8$ digit) add only $+5.9\%$ $R^2$ within EC. Summary statistics of zero distributions see arithmetic structure weakly ($|\rho| < 0.14$). The full zero vectors (not summary statistics) may carry more information.
    \item \textbf{The curvature prediction was wrong:} We predicted curvature would obstruct transfer; it facilitates it ($r = +0.27$). The parallel transport model is incorrect; nearest-neighbor clustering in curved regions is the mechanism.
\end{enumerate}

\subsection{Limitations}

\begin{enumerate}[nosep]
    \item The $1.57\times$ signal-to-null ratio for Arithmos, while statistically significant ($z = 149$), is modest. The secondary structure is real but not dominant.
    \item Calibration specificity is 33\% (1/3 known falsehoods rejected). The system is more permissive than desired.
    \item The phoneme projection is hand-designed, not learned. Different projection choices yield different signal ratios, though the cross-representation consistency (Mantel $r = 0.94$) suggests the underlying distance structure is robust.
    \item All results are on LMFDB and related datasets. Generalization to other mathematical databases is untested.
    \item The Euler characteristic is computed from a $k$-NN graph, which is a combinatorial approximation sensitive to $k$, sampling density, and noise. The true topology of the underlying data manifold may differ.
\end{enumerate}

\subsection{The Adversarial Ecosystem}

To continuously stress-test these claims, we built an autonomous adversarial system with four components: a Generator that invents attacks from 5 families (data, representation, structural, cross-domain, metric) with 20+ mutation operators; an Executor that runs the full measurement battery; a Judge that scores damage to core invariants; and an Archivist that logs and prioritizes the most damaging attacks. This system runs at 1.7 attacks/second and produces a daily report of what almost broke.

\subsection{Future Work}

Several directions would strengthen or refute the claims made here:

\begin{enumerate}[nosep]
    \item[(a)] \textbf{Learned embeddings.} Training variational autoencoders (VAEs) and contrastive learning models on the raw invariant data would test whether Megethos and Arithmos emerge as dominant latent axes in an unsupervised setting, without the hand-designed phoneme projection.
    \item[(b)] \textbf{Simple regression baselines.} Comparing cross-domain transfer against simple regression baselines (e.g., ridge regression, kernel regression) applied directly to raw invariants would quantify how much of the transfer signal is attributable to the phoneme projection versus the underlying data correlations.
    \item[(c)] \textbf{Random forest on raw features.} Training random forests on raw domain features without the phoneme projection would establish whether the coordinate system provides genuine compression, or whether equivalent transfer performance is achievable without any intermediate representation.
\end{enumerate}

\section{Conclusion}

We have found evidence for a two-dimensional coordinate system---Megethos (magnitude) and Arithmos (arithmetic group structure)---that provides a shared language for arithmetic--geometric mathematical objects across domains. The system enables cross-domain prediction at $\rho = 0.76$--$0.95$, generalizes out-of-distribution, and survives systematic adversarial testing in two independent representations.

The strongest defensible claim is: \emph{we observe a stable, low-dimensional coordinate system over arithmetic--geometric objects in which known invariants align and become mutually predictive across domains. The coordinate system is confirmed by two independent representations (94\% distance preservation), and enables directional transfer where denser neighborhoods correlate with better prediction.}

Whether this coordinate system is canonical, or merely one chart among many, remains open. The approximate rotational invariance in the Megethos--Arithmos plane and the representation dependence of the signal ratio suggest that while the \emph{distance structure} may be intrinsic, the \emph{coordinates} are not. Different mathematical ``cameras''---invariant-level and formula-level---see the same objects from different angles, with different dominant axes but the same pairwise distances and the same curvature sign. The distance structure is what is real.

\bibliographystyle{plain}
\begin{thebibliography}{99}
\bibitem{oseledets2011}
I.~V. Oseledets,
\newblock Tensor-train decomposition,
\newblock {\em SIAM J. Sci. Comput.}, 33(5):2295--2317, 2011.

\bibitem{oseledets2010}
I.~V. Oseledets and E.~E. Tyrtyshnikov,
\newblock TT-cross approximation for multidimensional arrays,
\newblock {\em Linear Algebra Appl.}, 432(1):70--88, 2010.

\bibitem{tntorch}
R.~Ballester-Ripoll, Y.~Lindstrom, and R.~Pajarola,
\newblock tntorch: Tensor network learning with {PyTorch},
\newblock {\em J. Mach. Learn. Res.}, 23(208):1--6, 2022.

\bibitem{iwaniec2000}
H.~Iwaniec and P.~Sarnak,
\newblock Perspectives on the analytic theory of {$L$}-functions,
\newblock {\em Geom. Funct. Anal.}, Special Volume, Part II:705--741, 2000.

\bibitem{lmfdb}
The LMFDB Collaboration,
\newblock The {L}-functions and modular forms database,
\newblock \url{https://www.lmfdb.org}, 2024.

\bibitem{knotinfo}
C.~Livingston and A.~H. Moore,
\newblock {KnotInfo}: Table of knot invariants,
\newblock \url{https://www.indiana.edu/~knotinfo}, 2024.

\bibitem{materialsproject}
A.~Jain et al.,
\newblock The {Materials Project}: A materials genome approach to accelerating materials innovation,
\newblock {\em APL Materials}, 1(1):011002, 2013.

\bibitem{oeis}
N.~J.~A. Sloane,
\newblock The {On-Line Encyclopedia of Integer Sequences},
\newblock \url{https://oeis.org}, 2024.

\bibitem{dokchitser}
T.~Dokchitser and V.~Dokchitser,
\newblock On the {B}irch--{S}winnerton-{D}yer quotients modulo squares,
\newblock {\em Ann. of Math.}, 172(1):567--596, 2010.

\bibitem{tensorrt}
NVIDIA Corporation,
\newblock TensorRT: High-performance deep learning inference optimizer,
\newblock \url{https://github.com/NVIDIA/TensorRT}, 2024.

\bibitem{thor}
Los Alamos National Laboratory,
\newblock Thor: Tensor decomposition library,
\newblock \url{https://github.com/lanl/thor}, 2024.

\bibitem{gap}
The GAP Group,
\newblock GAP -- Groups, Algorithms, and Programming,
\newblock \url{https://www.gap-system.org}, 2024.

\bibitem{bilbao}
M.~I. Aroyo et al.,
\newblock Bilbao Crystallographic Server,
\newblock \url{https://www.cryst.ehu.es}, 2024.

\bibitem{spglib}
A.~Togo and I.~Tanaka,
\newblock Spglib: a software library for crystal symmetry search,
\newblock \url{https://spglib.github.io/spglib/}, 2018.

\bibitem{pymatgen}
S.~P. Ong et al.,
\newblock Python Materials Genomics (pymatgen),
\newblock \url{https://pymatgen.org},
\newblock {\em Comput. Mater. Sci.}, 68:314--319, 2013.

\bibitem{fungrim}
F.~Johansson,
\newblock Fungrim: the Mathematical Functions Grimoire,
\newblock \url{https://fungrim.org}, 2024.
\end{thebibliography}

\end{document}
